We calculate in $n=4+\epsilon$ dimension to regularize all soft, collinear and ultraviolet poles. Unfortunaly this extension for \textit{polarized} processes is nontrivial, because the occuring Levi-Civita tensors $\varepsilon_{\mu\nu\rho\sigma}$ and $\gamma_5$. A common choice to deal with these objects is the HVBM prescription\cite{breitenlohner1977} that keeps those two objects four dimensional at the price of splitting the full $n$-dimensional space into a $(n-4)$-dimensional space, called \enquote{hat-space}, and a four-dimensional space (that is actually never used).

In leading order (LO) we have to consider the following processes
\begin{equation}
\Pggx(q) + \Pg(k_1) \rightarrow \PQ(p_1)+\PaQ(p_2)
\end{equation}
The corresponding parton structure tensor $W_{\mu\mu'}^{(0)}$ can then be written as
\fxerror{avoid all order expr?}
\begin{align}
&W_{\mu\mu'}^{(0)}(k_1,q;s,t_1,u_1,q^2;\sigma_{q})\nonumber\\
 &= \frac 1 2 E_\epsilon K_{\Pg\Pgg}\frac{1}{2s'}\!\int\!\frac{d^{n-1}p_1}{2E_1(2\pi)^{n-1}}\!\int\!\frac{d^{n-1}p_2}{2E_2(2\pi)^{n-1}}\delta(p_1^2-m^2) \delta(p_2^2-m^2)\nonumber\\
 &\hspace{20pt}(2\pi)^n\delta^{(n)}(k_1+q-p_1-p_2) \Md_{\mu}^{(0)}\Md_{\mu'}^{(0)}
\label{eq:PartonicStructureTensor0}\end{align}
where the initial $1/2$ is the initial state spin average, $K_{\Pg\Pgg}$ is the color average,
\begin{align}
E_\epsilon := \left\{\begin{array}{ll}
1/(1+\epsilon/2) &\text{unpolarized}\\
1 &\text{polarized}
\end{array}\right.
\end{align}
accounts for additional degrees of freedom in $n$ dimensions for initial bosons. The Lorentz indices $\mu$ and $\mu'$ refer to the virtual photon that is exchanged with the scattering lepton. We have chosen to detect the heavy \textit{antiquark} $\PaQ(p_2)$ and so we define the following Mandelstam variables:
\begin{equation}
s = (q+k_1)^2, \quad t_1=t-m^2=(k_1-p_2)^2-m^2, \quad u_1 = u - m^2 = (q-p_2)^2 -m^2 \label{eq:LOst1u1}
\end{equation}
For convenience we also define $s' = s-q^2$ and $u_1' = u_1 - q^2$. If the heavy \textit{quark} $\PaQ(p_1)$ is detected, $p_2$ in eq. (\ref{eq:LOst1u1}) has to be replaced by $p_1$ which effectively interchanges $t_1\leftrightarrow u_1$.\fxerror{move to LO?}

By using Lorentz covariance, hermiticity, parity invariance and current conservation the parton structure tensor can be decomposed into several parts:
\begin{align}
W_{\mu\mu'}(k_1,q;s,t_1,u_1,q^2;\sigma_{q}) &= \left(-g_{\mu\mu'} + \frac{q_\mu q_{\mu'}}{q^2}\right)\frac{d^2\sigma_T(s,t_1,u_1,q^2)}{dt_1du_1} \nonumber\\
 &\hspace{20pt} +\left(k_{1,\mu}-\frac{k_1\cdot q}{q^2}q_\mu\right)\left(k_{1,\mu'}-\frac{k_1\cdot q}{q^2}q_{\mu'}\right)\left(\frac{-4q^2}{{s'}^2}\right) \nonumber\\
 &\hspace{30pt} \cdot\left(\frac{d^2\sigma_T(s,t_1,u_1,q^2)}{dt_1du_1}+\frac{d^2\sigma_L(s,t_1,u_1,q^2)}{dt_1du_1}\right)
\end{align}
\fxerror{extend}
We can then define appropiate projection operators\cite{Laenen1993162,Vogelsang:1993eg}
\begin{align}
\hat {\mathcal P}^{\Pgg}_{G,\mu\mu'} &= -g_{\mu\mu'} &b_G(\epsilon) &= \frac 1 {2(1+\epsilon/2)}\\
\hat {\mathcal P}^{\Pgg}_{L,\mu\mu'} &= -\frac{4q^2}{{s'}^2} k_{1,\mu}k_{1,\mu'} &b_L(\epsilon) &= 1\\
\hat {\mathcal P}^{\Pgg}_{P,\mu\mu'} &= i\varepsilon_{\mu\mu'\rho\rho'}\frac{q^{\rho}k_1^{\rho'}}{s'} &b_P(\epsilon) &= 1
\end{align}
\fxerror{justify avoidance of $\Delta$?} and we then find
\begin{align}
\frac{d^2\sigma_{k}(s,t_1,u_1,q^2)}{dt_1tu_1} &= b_k(\epsilon)\hat {\mathcal P}^{\Pgg}_{k,\mu\mu'}W^{\mu\mu'}
\end{align}
with $k\in\{G,L,P\}$ denoting (here and mostly ever after) the projection type. The transverse partonic cross section $d\sigma_T$ can be reconstructed from the above definitions by using
\begin{align}
d\sigma_T &= d\sigma_G + b_G(\epsilon)d\sigma_L
\end{align}
We also define accordingly
\begin{equation}
E_G(\epsilon) = E_L(\epsilon) = \frac 1 {1+\epsilon/2} \qquad E_P(\epsilon) = 1
\end{equation}

The final state spins are always summed over, but the initial spins have to be treated seperately: for unpolarized projections $k\in\{G,L\}$ they are also summed over, but for the polarized projection $k=P$ they are projected on their asymmetric part:
\begin{align}
\hat {\mathcal P}^{\Pg}_{G,\nu\nu'} = \hat {\mathcal P}^{\Pg}_{L,\nu\nu'} &= -g_{\nu\nu'} &\hat {\mathcal P}^{\Pg}_{P,\nu\nu'} &= 2i\epsilon_{\nu\nu'\rho\rho'}\frac{k_1^{\rho}q^{\rho}}{s'}\label{eq:PgG}
\end{align}
where $\nu$ and $\nu'$ refer to the initial gluon. By writing $\hat {\mathcal P}^{\Pg}_{G,\nu\nu'}$ in eq. (\ref{eq:PgG}) we decided to introduce Fadeev-Popov ghosts\cite{Bojak:2000eu} as we got a single diagram in next-to-leading order with a triple-gluon vertex\fxerror{explain ghosts?}. As we can consider all quarks in the initial state as massless, we further find
\begin{align}
\hat {\mathcal P}^{\Pq}_{G,aa'} = \hat {\mathcal P}^{\Pq}_{L,aa'} &= \left(\slashed k_1\right)_{aa'}
&\hat {\mathcal P}^{\Pq}_{P,aa'} &= -\left(\gamma_5\slashed k_1\right)_{aa'}\\
\hat {\mathcal P}^{\Paq}_{G,bb'} = \hat {\mathcal P}^{\Paq}_{L,bb'} &= \left(\slashed k_1\right)_{bb'}
&\hat {\mathcal P}^{\Paq}_{P,bb'} &= \left(\gamma_5\slashed k_1\right)_{bb'}
\end{align}
where $a$ and $a'$ refer to the Dirac-index of the intial quark in next-to-leading order - analogous for $b$ and the antiquark.

We further define a set of partonic variables:
\begin{align}
0\leq&\,\rho = \frac {4m^2} s\leq 1 &0\leq&\,\beta = \sqrt{1-\rho}\leq 1 &0\leq&\,\chi = \frac{1-\beta}{1+\beta}\leq 1\\
&\rho_q = \frac {4m^2} {q^2}\leq 0 &1\leq&\,\beta_q = \sqrt{1-\rho_q} &0\leq&\,\chi_q = \frac{\beta_q-1}{\beta_q+1}\leq 1
\end{align}

When computing Feynman diagrams a computer algebra system (CAS) is almost obligatory: common choices are \texttt{FORM}\cite{Vermaseren:2000nd} or \MMa\cite{Mathematica} - for the later the most common choice is \texttt{TRACER}\cite{Tracer}, but we have chosen \HEPMath\cite{wiebusch_hepmath_2015}. We used the Feynman rules given by \cite{Leader} and \cite{Bojak:2000eu}.
